---
title: "R Notebook"
output: html_notebook
---
#create a new column in mtcars having values "Yes/No" for wt less than median
```{r}
mtcars_wt = mtcars
mtcars_wt$wt_check = NA
mtcars_wt$wt_check = ifelse(mtcars_wt$wt < median(mtcars_wt$wt), 'Yes', 'No')
mtcars_wt
```

#create a new column in mtcars having values "Yes/No" for gear value equals 5
```{r}
mtcars_gear = mtcars
mtcars_gear$gear_check = NA
mtcars_gear$gear_check = ifelse(mtcars_gear$gear ==5, 'Yes' , 'No')
mtcars_gear
```

#print mtcars names that start with "F"
```{r}
mtcars_rownames = rownames(mtcars)

for(i in seq(1,length(mtcars_rownames)))
{
  rname = substring(mtcars_rownames[i], 1, 1)
  if(rname == 'F')
  {
    print(mtcars_rownames[i])
  }
}
```
#Alternate way excluding for loop
```{r}
mtcars_rownames = rownames(mtcars)

mtcars_rownames[substr(mtcars_rownames,1,1)=='F']
```

#Check the gear value in mtcars for all rows if it is 1/2/3/4/5 and print the value
```{r}
for(i in seq(1,length(mtcars_rownames)))
{
  gear_num = mtcars_gear$gear[i]
  print(switch(gear_num, 'Gear is 1', 'Gear is 2' , 'Gear is 3', 'Gear is 4', 'Gear is 5'))
}
```
#Print even numbers from 1-5 using switch statement
```{r}
for(i in 1:5)
  if (i %% 2 == 0)
  {
  print(switch(i, 'I am 1', 'I am 2' , 'I am 3', 'I am 4'))
  }
```
#Print sum of all mpg and gear values in mtcars using While stmt
```{r}
i=1
sum_mpg = 0 
sum_gear =0
mtcars_mpg = mtcars
while(i <= length(mtcars_rownames))
{ 
  sum_mpg = sum_mpg + mtcars_mpg$mpg[i]
  sum_gear = sum_gear + mtcars_gear$gear[i]
  i=i+1
}

print(paste("sum of all gear" , sum_gear))
print(paste("sum of all mpg" , sum_mpg))

```
```{r}
mtcars
```


